\documentclass[listof=totocnumbered,bibliography=totocnumbered,12pt,oneside]{scrreprt}
\def\@afterindentfalse{\let\if@afterindent\iffalse}
\usepackage[english,german,ngerman]{babel}
\usepackage{geometry}
\usepackage{xltxtra}
\usepackage{lmodern}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{chngcntr}
\usepackage{amsmath,amsfonts}
\usepackage{fancyvrb}
\usepackage{minted}
\usepackage{color}
\usepackage{url}
\usepackage{setspace}
\usepackage[noindentafter]{titlesec}
\usepackage{titletoc}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{subfig}

\newfontfamily\headingfont[]{Avenir Heavy}
\definecolor{codebg}{rgb}{0.8,0.8,0.9}
\newminted{c++}{linenos=true,bgcolor=codebg,tabsize=4,showspaces=false}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\counterwithout{footnote}{chapter}
\numberwithin{equation}{subsection}
\renewcommand\theequation{\arabic{equation}}
\setmainfont[Mapping=tex-text]{Avenir Book}
\setsansfont{Avenir Book}
\titleformat{\tableofcontents}{\Large\bfseries}{\headingfont}{0em}{}
\titleformat{\chapter}{\Large\bfseries}{\headingfont}{0em}{\thechapter\hspace{1em}}
\titleformat{\section}{\large\mdseries}{\headingfont}{0em}{\thesection\hspace{1em}}
\titleformat{\subsection}{\normalsize\mdseries}{\headingfont}{0em}{\thesubsection\hspace{1em}}
\titlespacing{\paragraph}{0pt}{3.5ex plus 1ex minus .2ex}{0pt}
\linespread{1.3}

\lhead[O,E]{}
\rhead[O,E]{Door Tracked AR}
\lfoot[O,E]{Seite \thepage\ von \pageref{LastPage}}
\cfoot[O,E]{}
\rfoot[O,E]{Kron, Ilic}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\fancypagestyle{plain}{
	\lhead[O,E]{}
	\rhead[O,E]{Door Tracked AR}
	\cfoot[O,E]{}
	\rfoot[O,E]{Kron, Ilic}
}

\begin{document}
\pagestyle{fancy}

\subject{Bachelor-Thesis}
\title{Door Tracked Augmented Reality}
\author{Mato Ilic \and David Kron}
\date{Januar 2014}
\publishers{Betreuer: Marcus Hudritsch\\Experte: Andreas Dürsteler}

\maketitle

\tableofcontents
\newpage

\include{contents/abstract}
\newpage

\include{contents/ziele}
\newpage

\include{contents/grundlagen}
\newpage

\include{contents/tuererkennung}
\newpage

%\include{contents/umsetzung}
%\newpage

\include{contents/projektion}
\newpage

\include{contents/opengl}
\newpage

\include{contents/resultat}
\newpage

\include{contents/fazit}
\newpage


\newpage
\begin{thebibliography}{5}

\bibitem {learningopencv}
Bradski, Gary / Kaehler Adrian:
Learning OpenCV: Computer Vision with the OpenCV Library.
Sebastopol: O'Reilly Media, Inc.

\bibitem {zhang}
Zhang, Zhengyou (1998): A Flexible New Technique for Camera Calibration. 
Redmond: Microsoft Research.

\bibitem {escalera}
de la Escalera, Arturo / María Armingol, Jose: Automatic Chessboard Detection for Intrinsic and Extrinsic Camera Parameter Calibration. 
Madrid: Universidad Carlos III de Madrid.

\bibitem {kiryati}
N. Kiryati, Y. Eldar, A.M. Bruckstein:
A probabilistic Hough transform, Pattern Recognition 
Volume 24, Issue 4, 1991, Pages 303-316, ISSN 0031-3203, DOI: 10.1016/0031-3203(91)90073-E. 

\bibitem {nieto}
Nieto, Marcos (2011): Line segment detection using weighted mean shift procedures on a 2D slice sampling strategy
London: Springer

\bibitem {bresenham}
Bresenham, Jack (1965): Algorithm for computer control of a digital plotter. 
USA: IBM

\bibitem {zhangrectification}
Zhang, Zhengyou (2002): Single-View Geometry of A Rectangle With Application to Whiteboard Image Rectification.
Redmond: Microsoft Research.

\bibitem {simek}
Simek, Kyle: Calibrated Cameras in OpenGL without glFrustum. Stand 03. Juni 2013. $http://ksimek.github.io/2013/06/03/calibrated_cameras_in_opengl$  (aufgerufen am 16. Januar 2013).


\end{thebibliography}

\newpage
\chapter{Ehrlichkeitserklärung}
Hiermit bestätigen die Autoren, diese Arbeit ohne fremde Hilfe und unter Einhaltung der gebotenen Regeln erstellt zu haben.
\\
\\
\\
\textbf{Mato Ilic}
\\
\\
\\
\rule{0.85\textwidth}{0.4pt} \\
Ort, Datum \hspace * {5cm} Unterschrift
\\
\\
\\
\textbf{David Kron}
\\
\\
\\
\rule{0.85\textwidth}{0.4pt} \\
Ort, Datum \hspace * {5cm} Unterschrift

\end{document}
